Reproducibility in plant pathology: where do we stand and a way forward

### 2021-07-02 analysis/paper/paper.Rmd
Corrects filepaths for figure outputs after embedding fonts

# put them all together
p <- (A | B) / (C | D)
p <- p + plot_annotation(tag_levels = "A")
ggsave(filename = "../figures/Sparks et al Figure 1.eps",
       plot = p,
       device = "eps",
       width = 6,
       height = 6,
       units = "in")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 1.eps"),
   outfile = ("figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 2.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("figures/Sparks et al Figure 2eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

>>>>

# put them all together
p <- (A | B) / (C | D)
p <- p + plot_annotation(tag_levels = "A")
ggsave(filename = "../figures/Sparks et al Figure 1.eps",
       plot = p,
       device = "eps",
       width = 6,
       height = 6,
       units = "in")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 1.eps"),
   outfile = ("../figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 2.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("../figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```
